Capitalized Title Here

### 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
code side-by-side?

```{r, eval=FALSE}
sig.plot$segment_shift_plot
```

>>>>

\hh{XXX Could we move the code into the corresponding figure and show the relevant pieces side by side? I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}
```{r, eval=FALSE}
sig.plot$segment_shift_plot
```
